Transfer report

### 2019-02-06 Report/final-results.Rmd
Updated results

```{r}

walk_all_filtered <- rbind(sub_walk_all, sub_walk_all_2)
ggplot(only_blocks(walk_all_filtered, 6), aes(x = condition, y = min_norm_distance, fill = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average path distance in the last block of the transfer phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F)

ggplot(only_blocks(walk_all_filtered, 6), aes(x = condition, y = errors, fill = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Number of visiting errors in the last block of the transfer phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F)
```

>>>>

```{r}
ggplot(only_blocks(walk_all, 6), aes(x = condition, y = min_norm_distance, fill = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Average path distance in the last block of the transfer phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F)

ggplot(only_blocks(walk_all, 6), aes(x = condition, y = errors, fill = learning.condition)) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(0.95), geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_dodge(width=0.95),geom="bar") +
  ylab("Number of visiting errors in the last block of the transfer phase") + xlab("Condition") + 
  scale_fill_manual(values = estimote_pal, "Condition")  + guides(fill=F)
```
